### 2023-04-30 chapter2/chapter2.tex
Updated discussion paragraphs in outline
Added final paragraphs to discussion section

% V. OU analyses
% In summary, both the phylogenetic comparative and simulation-based methods have their strengths and weaknesses. The BM and OU models are powerful models of generic trait evolution, and therefore can describe However, because simulation-based approaches can fully specify the mechanisms and constraints of IDR evolution, they permit tests of increasingly refined models of IDR evolution. We therefore view the two approaches are complementary, and propose the use of hybrid methods test statistics derived from phylogenetic comparative methods like the BM model and simulations to generate the null distributions for those test statistics. Because the simulations are more specific and time-consuming, we recommend future investigators begin using
%    C. Because
%        1. Weaknesses are explicit assumptions about substitution and indel processes and high computational cost
%        2. Is also a strength because allows testing of increasingly specific hypotheses for IDR evolution
%        3. Complementary approach -- fewer assumptions about description of evolution but cannot be tailored to specific hypotheses
%        4. Hybrid approach using comparisons of rates as the statistical test and simulations to generate the null distribution
%    D. Another hybrid approach is using permutation-like tests to test for the conservation of patterned features like omega or motifs
%        1. Uses background distribution of amino acids in each IDR, so can specifically test for importance of patterning based features.
%        2. We expect that IDRs evolve under multiple regimes where some are unconstrained and others are constrained with compositional and patterned features, or a mixture of both. As a battery of statistical methods will be necessary to tease apart these details, we view these approaches as complementary, each with its own strengths and weaknesses.
%    E. Thus, while these results represent a significant step forward in relating sequence to function in IDRs, further studies exploring these approaches will undoubtedly reveal new insights into these pervasive but poorly understood regions of proteins.

@@

>>>>

@@

While the BM and OU models are powerful tools for studying trait evolution, their generality limits the specificity of the hypotheses they can test. In contrast, because simulation-based approaches can specify arbitrary constraints, they permit investigations of increasingly refined models of IDR evolution. We therefore view the two approaches as complementary, and propose the use of hybrid methods where test statistics are derived from phylogenetic comparative methods like the BM model, and simulations generate the null distributions for those test statistics. While simulations can eliminate specific hypotheses, the substantial resources involved both in designing them and generating samples make exhaustively testing mechanisms of feature constraint by simulation impractical. We instead recommend a workflow that begins with an analysis using generic models of trait evolution to suggest specific hypotheses of constraint that are then tested with a simulation-based approach. Another hybrid method involves using sequence permutations to test for the conservation of motifs or patterned features like kappa. In this method, a comparative model like BM provides the test statistic as before, and a sample of shuffled sequences approximates the null distribution. Because the background distribution of residues is preserved, this approach can specifically test for the conservation of motifs or patterned features in an IDR independent of the conservation of its composition.

However, as IDRs likely evolve under multiple selective regimes where the constraint of different compositional, patterned, or motif features is highly specific to each, we expect a combination of statistical and computational methods will be needed to disentangle the complex forces driving IDR evolution. Accordingly, while these results represent a significant step forward in relating sequence to function in IDRs, further studies exploring these and other approaches will undoubtedly reveal new insights into these pervasive but poorly understood regions of proteins.
